TODO title

### 2017-01-20 doc/paper/paper.tex
Added IA parameters to table

\subsection{Metrics}
To test and compare the two WTA mechanisms we provide an input of $\rho_i 
= u - s \delta_{1i} + \eta_i$ where $u$ is the strength of the strongest input, 
$s$ the target separation to all other inputs, $\delta$ the Kronecker delta, and 
$\eta_i$ Gaussian white noise with standard deviation $\sigma$. Thus, without 
loss of generality, the first state variable receives the strongest input and 
all other state variables receive input that is smaller by $s$. We chose this 
input as for $\rho_i \rightarrow 0$ the influence of input $\rho_i$ will 
decrease and the effective number of choices to decide between would decrease  
As $s \rightarrow 0$ the problem gets more difficult. We will use $u = 1$ as 
long as not indicated otherwise and set the number of dimension to $d = 10$.  In 
both WTA models we use 200 neurons for each dimensions. In the IA network this 
are split as 150 neurons for each layer 1 population and 50 neurons for each 
layer 2 population. Further parameters are summarized in Table~\ref{tbl:params}.
\begin{table}
    \caption{Summary of parameter values.}\label{tbl:params}
    \begin{tabular}{ll}
        LCA time constant & $\tau = \SI{0.1}{\second}$ \\
        LCA recurrency parameters & $k = \beta = 1$ \\
        IA accumulation time constant & $\tau_1 = \SI{0.1}{\second}$ \\
        IA feed-back time constant & $\tau_2 = \SI{0.1}{\second}$ \\
        IA threshold & $\vartheta = 0.8$ \\
        Recurrent synaptic time constant & $\tau_{\mathrm{s}} 
        = \SI{0.1}{\second}$ \\
        Feed-forward synaptic time constant & $\tau_{\mathrm{s}} 
        = \SI{0.005}{\second}$ \\
        Output decoding synaptic time constant & $\tau_{\mathrm{s}} 
        = \SI{0.01}{\second}$
    \end{tabular}
\end{table}

>>>>

\subsection{Metrics}
To test and compare the two WTA mechanisms we provide an input of $\rho_i 
= u - s \delta_{1i} + \eta_i$ where $u$ is the strength of the strongest input, 
$s$ the target separation to all other inputs, $\delta$ the Kronecker delta, and 
$\eta_i$ Gaussian white noise with standard deviation $\sigma$. Thus, without 
loss of generality, the first state variable receives the strongest input and 
all other state variables receive input that is smaller by $s$. We chose this 
input as for $\rho_i \rightarrow 0$ the influence of input $\rho_i$ will 
decrease and the effective number of choices to decide between would decrease  
As $s \rightarrow 0$ the problem gets more difficult. We will use $u = 1$ as 
long as not indicated otherwise and set the number of dimension to $d = 10$.  In 
both WTA models we use 200 neurons for each dimensions. In the IA network this 
are split as 150 neurons for each layer 1 population and 50 neurons for each 
layer 2 population. Further parameters are summarized in Table~\ref{tbl:params}.
\begin{table}
    \caption{Summary of parameter values.}\label{tbl:params}
    \begin{tabular}{ll}
        LCA time constant & $\tau = \SI{0.1}{\second}$ \\
        LCA recurrent parameters & $k = \beta = 1$ \\
        IA accumulation time constant & $\tau_1 = \SI{0.1}{\second}$ \\
        IA feed-back time constant & $\tau_2 = \SI{0.1}{\second}$ \\
        IA threshold & $\vartheta = 0.8$ \\
        IA recurrent parameters & $\lambda = 1, \bar{\beta} = 2$ \\
        Recurrent synaptic time constant & $\tau_{\mathrm{s}} 
        = \SI{0.1}{\second}$ \\
        Feed-forward synaptic time constant & $\tau_{\mathrm{s}} 
        = \SI{0.005}{\second}$ \\
        Output decoding synaptic time constant & $\tau_{\mathrm{s}} 
        = \SI{0.01}{\second}$
    \end{tabular}
\end{table}
